Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-04-25 manuscript/cpcrw_manuscript.Rmd
Fixed "<0.001" problem in table p-values
Thanks @apeyton

pclean <- function(x) {  # pretty formatting of p-values
  ifelse(x < 0.001, "< 0.001", paste("=", formatC(x, digits = 3, format = 'f'))) %>%
    paste("P", .)
}

@@

```{r table1, echo=FALSE}
knitr::kable(summary(step_co2_lme)$tTable, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

@@

```{r table2, echo=FALSE}
knitr::kable(summary(step_ch4_lme)$tTable, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

>>>>

pclean <- function(x, digits = 3, printP = TRUE) {  # pretty formatting of p-values
  ltstring <- paste0("< 0.", substr("000000000", 1, digits - 1), "1")
  valstring <- ifelse(x < 10^-digits, ltstring, formatC(x, digits = digits, format = 'f'))
  if(printP) {
    ifelse(x < 0.001, valstring, paste("=", valstring)) %>% paste("P", .)
  } else {
    valstring
  }
}

@@

```{r table1, echo=FALSE}
t1 <- summary(step_co2_lme)$tTable %>% round(3) %>% as.data.frame()
t1$`p-value` <- pclean(t1$`p-value`, printP = FALSE)
knitr::kable(t1, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

@@

```{r table2, echo=FALSE}
t2 <- summary(step_co2_lme)$tTable %>% round(3) %>% as.data.frame()
t2$`p-value` <- pclean(t2$`p-value`, printP = FALSE)
knitr::kable(t2, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```
